Using NSGA-II to compose model transformations alternatives

### 2014-11-05 SysCon_article/article_syscon.tex
suppresion of LaTex warnings

\begin{abstract}
The size and complexity of modern systems is rapidly increasing. Meanwhile, the ability to understand and maintain such systems is decreasing almost as fast.
Model Driven Engineering promotes the automation of design activities by means of model transformations, enabling to cope with systems complexity. However, the design space produced by the composition of these model transformations is difficult to explore automatically. The main reason that makes this exploration difficult is the size of the design space: the number of possible design choices grows exponentially with the number of model transformation alternatives.
This paper presents a MDA approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems. This approach allows the system architects to automatically select the most adequate model transformations compositions by using multi-objectives optimization evolutionary algorithms.

@@

\section{Introduction}

Nowadays, modern systems become more and more large and complex and therefore more difficult to develop and maintain. For example, embedded critical systems such as avionic, railway and automotive are often built to guarantee the safety and robustness properties. To meet these challenging properties makes the design of embedded systems very complex.

Model Driven Engineering (MDE) proposes the use of models as the key assets in the development of such systems. These models cover the whole system development cycle. They can be manipulated manually or automatically using model transformations. These transformations aims to enhance portability by way of separating system (abstract) architecture from platform (concrete) architecture. They facilitate the development of a system in abstraction, and simplifies implementation of that system across a variety of target platforms. In this work, we use model transformations to model design alternatives of the system. This process will help system architects to predict Non-Functional Properties (NFP) of a system before its development\cite{1291833}. This prediction can be exploited to drive decisions about which components should be used and how they should be connected so as to meet the NFP imposed on the design.

%Even though MDE is being successfully applied in many scenarios, it still needs appropriate mechanisms to handle the development of complex, large-scale systems. One such mechanism is a facility to make transformations reusable, so that we can apply them to different contexts.

@@

\subsection{Mapping model transformation alternatives into a multiple-objectives optimization problem}
\label{Adapting}
The next step of our approach consist in using model transformations compositions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem (MOOP). Where the population to optimize or the design space represent a set of model transformations alternatives and the objectives to fulfils are NFP such as reliability, availability and response time. The integration process is described in the following sections.

@@

Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes MTA1 and MTA2 respectively composed of the following genes \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce new genomes MTA12 and MTA21, respectively composed of new sequences \{TRA21,TRA12,TRA13\} and \{TRA11,TRA22,TRA23\}. This operator combines MTA1 and MTA2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.

>>>>

\begin{abstract}
The size and complexity of modern systems is rapidly increasing. Meanwhile, the ability to understand and maintain such systems is decreasing almost as fast.
Model Driven Engineering promotes the automation of design activities by means of model transformations, enabling to cope with systems complexity. However, the design space produced by the composition of these model transformations is difficult to explore automatically. The main reason that makes this exploration difficult is the size of the design space: the number of possible design choices grows exponentially with the number of model transformation alternatives.
This paper presents a Model Driven Engineering approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems. This approach allows the system architects to automatically select the most adequate model transformations compositions by using multi-objectives optimization evolutionary algorithms.

@@

\section{Introduction}
Nowadays, modern systems become more and more large and complex and therefore more difficult to develop and maintain. For example, embedded critical systems such as avionic, railway and automotive are often built to guarantee the safety and robustness properties. To meet these challenging properties makes the design of embedded systems very complex.

Model Driven Engineering (MDE) proposes the use of models as the key assets in the development of such systems. These models cover the whole system development cycle. They can be manipulated manually or automatically using model transformations. These transformations aims to enhance portability by way of separating system (abstract) architecture from platform (concrete) architecture. They facilitate the development of a system in abstraction, and simplifies implementation of that system across a variety of target platforms. In this work, we use model transformations to model the system design alternatives. This process will help system architects to predict Non-Functional Properties (NFP) of a system before its development\cite{1291833}. This prediction can be exploited to drive decisions about which components should be used and how they should be connected so as to meet the NFP imposed on the design.

@@

\subsection{Mapping model transformation alternatives into a multiple objectives optimization problem}
\label{Adapting}
The next step of our approach consist in using model transformations compositions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem (MOOP). Where the population to optimize or the design space represent a set of model transformations alternatives and the objectives to fulfils are NFP such as reliability, availability and response time. The integration process is described in the following sections.

@@

Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes MTA1 and MTA2 respectively composed of the following genes \{TRA11, TRA12, TRA13\} and \{TRA21, TRA22, TRA23\} to produce new genomes MTA12 and MTA21, respectively composed of new sequences \{TRA21,TRA12,TRA13\} and \{TRA11,TRA22,TRA23\}. This operator combines MTA1 and MTA2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
